\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-27 syntax.tex
comments

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\sigma}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\sigma~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\sigma~R)}
\quad n < N
}
{\goodTerm{\Gamma}{"prjR"~n~o}{("RecSig1"~(\pi_1^n \sigma)~(\pi_2^n \sigma)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodType{\Gamma}{T}{\bW \sigma}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\sigma~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}
$$

In our meta-theory, for simplicity we only formulate non-dependent eliminators, i.e.,
\textit{recursors}.
%\YZ{Do dependent eliminators pose technical difficulties, or do you avoid them solely because they require more verbiage?}\EDJreply{I don't think there is technical difficulties to do that. The formulation of course will be much more horrifying if use dependent eliminator here. } 
Like our plugin implementation, each recursor is constructed by a linkage containing handlers dealing with each
constructor and code reuse for recursor is delegated to linkage
inheritance. This greatly simplifies the metatheory development.

Intuitively \ruleref{Hdler} is indicating the type of recursor handler
for one specific constructor, and \ruleref{Hdlers} is the linkage type
of the bundle of all recursor handlers of one given inductive type. We
omit the definition of "RecSig" but \ruleref{Hdler-Proj} indicates its
(apparent) internal definition. "prjR" is also the handler selection
from the handler linkage, and is helpful for the formulation of
$\beta$-rule of "Wrec" (omitted here). Finally \ruleref{Rec-Constr} is
used to construct a concrete recursor given a specific linkage of aggregated
handlers. All these rules satisfy substitution laws and omitted here. Thus, we are still using \textit{decoupling} of the syntax of the case
handlers and exhaustiveness checking to resolve
\ref{chg:extensible-inductive-type}.

>>>>

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\sigma}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\sigma~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\sigma~R)}
\quad n < N
}
{\goodTerm{\Gamma}{"prjR"~n~o}{("RecSig1"~(\pi_1^n \sigma)~(\pi_2^n \sigma)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodType{\Gamma}{T}{\bW \sigma}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\sigma~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}\YZ{
(1) Use \tau for inductive types and \sigma for linkage signatures.
(2) Try using the same metavariables (j and n) as in the rules on W-types.
(3) In Rec-Constr, no checking of \Gamma \vdash T : \bW \tau?
(4) Why are RecSig1, RecSig, Wrec, prjR not listed in the syntax figure?
}
$$

In our metatheory, for simplicity we only formulate non-dependent eliminators, i.e.,
\textit{recursors}.
%\YZ{Do dependent eliminators pose technical difficulties, or do you avoid them solely because they require more verbiage?}\EDJreply{I don't think there is technical difficulties to do that. The formulation of course will be much more horrifying if use dependent eliminator here. } 
Like our plugin implementation, each recursor is constructed by a
linkage containing handlers dealing with each constructor, and code
reuse for recursor is delegated to linkage inheritance.
This greatly simplifies the metatheory development.

Intuitively \ruleref{Hdler} is indicating the type of recursor handler
for one specific constructor, and \ruleref{Hdlers} is the linkage type
of the bundle of all recursor handlers of one given inductive type. We
omit the definition of "RecSig" but \ruleref{Hdler-Proj} indicates its
(apparent) internal definition. "prjR" is also the handler selection
from the handler linkage, and is helpful for the formulation of
$\beta$-rule of "Wrec" (omitted here). Finally \ruleref{Rec-Constr} is
used to construct a concrete recursor given a specific linkage of aggregated
handlers. All these rules satisfy substitution laws, which are omitted here.
Thus, we are still using \textit{decoupling} of the syntax of the case
handlers and exhaustiveness checking to resolve
\ref{chg:extensible-inductive-type}.
